Learning constraints in tabular data

### 2016-05-20 Paper/ECAI/tabular.tex
Reworked intro algorithm

\newcommand{\constraints}{\ensuremath{\mathcal{T}}\xspace}
\newcommand{\format}[1]{\textit{#1}\xspace}
\newcommand{\generategroups}{\format{generateGroups}}
\newcommand{\extractgroups}{\format{extractGroups}}
\newcommand{\extracttables}{\format{extractTables}}
\newcommand{\learnconstraints}{\format{learnConstraints}}
\newcommand{\findassignment}{\format{findConstraints}}
\newcommand{\postprocess}{\format{pruneRedundant}}
\newcommand{\constrainttorder}{\format{templateOrder}}
\newcommand{\template}{\format{constraint template}}
\newcommand{\sname}{\format{TaCLe}}

@@

\paragraph{Rest old text}

This section describes our approach to \tcl. The main method takes \textit{groups} and {\template}s as input, and is described in Section~\ref{sec:algo}. We first explain how tables and groups can be extracted from raw spreadsheet data.

@@

\begin{algorithm}[t]
  \begin{algorithmic}
    \footnotesize
    \State \textbf{Input:} $\groups$ -- groups, $\constraints$ -- \template's, \dependencies -- dependency graph
    \State \textbf{Output:} $C$ -- learned constraints
    \State $C \gets \emptyset$ %\Comment{The set of constraints}
  \ForAll{$s \in \constrainttorder(\constraints,\dependencies)$}
  \State $n \gets$ number of arguments of template $s$
    \ForAll{$(G_1, \dots, G_n) \in \generategroups(s, \groups, C)$}
      \State $C \gets C \cup \findassignment(s, (G_1, \dots, G_n))$
    \EndFor
  \EndFor\\
\Return $C$
\end{algorithmic}
\caption{Tabular constraint learning}
\label{algo:tcl}
\end{algorithm}

The pseudo-code of the main method is shown in Algorithm~\ref{algo:tcl}; it consists of three key components: 1) templates can depend on each other, so they are ordered to avoid having to verify the same template multiple times; 2) we generate all combinations of superblocks that can satisfy the signature using constraint satisfaction techniques; 3) from this, all satisfying subblocks are generated.
We now describe each of the three components in more detail.

\samuel{MARKER-C}
\subsubsection{Template ordering}
As discussed before, a constraint may imply another constraint. This is apparent when looking at the template signatures in Table~\ref{table:constraints}, where one can see that some signatures depend on other constraints, such as $LOOKUP$ depending on $FOREIGNKEY$.

% not helpful:
%The \ecrank{v_y}{v_x} constraint does not have any dependencies, however in a restricted version without ties, groups assigned to $v_y$ would always be a permutation of numbers $1, 2, ..., \textit{length}(v_y)$.

@@

\subsection{Implementation}
We provide some more details of our implementation of the above algorithmic approach, to ease reproducibility.

>>>>

\newcommand{\constraints}{\ensuremath{\mathcal{T}}\xspace}
\newcommand{\format}[1]{\textit{#1}\xspace}
\newcommand{\generategroups}{\format{SuperblockAssignments}}
\newcommand{\extractgroups}{\format{extractGroups}}
\newcommand{\extracttables}{\format{extractTables}}
\newcommand{\learnconstraints}{\format{LearnConstraints}}
\newcommand{\findassignment}{\format{FindSubassignments}}
\newcommand{\postprocess}{\format{pruneRedundant}}
\newcommand{\constrainttorder}{\format{templateOrder}}
\newcommand{\template}{\format{constraint template}}
\newcommand{\sname}{\format{TaCLe}}

@@

@@

\begin{algorithm}[t]
  \begin{algorithmic}
    \footnotesize
    \State \textbf{Input:} $\groups$ -- groups, $s$ -- constraint template
    \State \textbf{Output:} $C$ -- learned constraints
    \Procedure{LearnConstraints}{$\groups$, $s$}
    \State $C \gets \emptyset$ %\Comment{The set of constraints}
    \State $n \gets$ number of arguments of template $s$
    \State $A \gets \generategroups(s, \groups)$
    \ForAll{$(B_1, \dots, B_n) \in A$}
      \ForAll{$(B_1', \dots, B_n') \in \findassignment(s, (B_1, \dots, B_n))$}
        \State $C \gets C \cup \{ s(B_1', \dots, B_n') \}$
      \EndFor
    \EndFor
\Return $C$
\EndProcedure
\end{algorithmic}
\caption{Learn tabular constraints}
\label{algo:tcl}
\end{algorithm}

The pseudo-code of the main method is shown in Algorithm~\ref{algo:tcl}.
Given a constraint template~$s$, the algorithm first generates all combinations of superblocks (i.e. superblock assignments) that are consistent with the signature.
In a second step it looks at every superblock assignment and finds subassignments that satisfy the signature and definition of~$s$.

@@

\subsection{Implementation}

\samuel{Start: Moved template ordering}
\subsubsection{Template ordering}
As discussed before, a constraint may imply another constraint. This is apparent when looking at the template signatures in Table~\ref{table:constraints}, where one can see that some signatures depend on other constraints, such as \textit{LOOKUP} depending on \textit{FOREIGNKEY}.

% not helpful:
%The \ecrank{v_y}{v_x} constraint does not have any dependencies, however in a restricted version without ties, groups assigned to $v_y$ would always be a permutation of numbers $1, 2, ..., \textit{length}(v_y)$.
\samuel{End: Moved template ordering}

We provide some more details of our implementation of the above algorithmic approach, to ease reproducibility.
